Pairwise-complete correlation considered dangerous

### 2015-05-27 missing.Rmd
Updated missing note

The functions `V=cov(x)` computes the symmetric covariance matrix `V` with entries defined by the pairwise covariance of columns of `x`,
$$
\mathsf{V}[i,j] = covariance (\mathsf{x}[,i], \,\,\,\mathsf{x}[,j]),
$$
where $i=j=1,2,3$ in this example. The function `cor(x)` similarly computes the symmetric correlation matrix with entries defined by pairwise correlation of the columns of `x`. For example:
```{r}
cov(x)
cor(x)
```
Due to missing values in the third column of `x` we know that we don't know the
covariance between `x[,3]` and anything else. Thanks to an arguably
questionable^[The `cov2cor` function used by `cor` always puts ones along the
diagonal of a correlation matrix; that choice is valid only if all unknowns may
assume bounded and valid numeric values which is actually pretty reasonable. But worse and weirder than that, R is inconsistent: `cor(x[,3],x[,3])` returns `NA` (!!!!)] choice in R's
`cov2cor` function, we see that `cor(x[,3],x[,3])=1`, but we don't know the
correlation between `x[,3]` and the other columns.

>>>>

The functions `V=cov(x)` computes the symmetric covariance matrix `V` with entries defined by the pairwise covariance of columns of `x`,
$$
\mathsf{V}[i,j] = covariance (\mathsf{x}[,i], \,\,\,\mathsf{x}[,j]),
$$
where $i=j=1,2,3$ in this example. The function `cor(x)` similarly computes the symmetric correlation matrix with entries defined by pairwise correlation of the columns of `x`. For example:
```{r}
cov(x)
cor(x)
```
Due to missing values in the third column of `x` we know that we don't know the
covariance between `x[,3]` and anything else. Thanks to an arguably
questionable^[The `cov2cor` function used by `cor` always puts ones along the
diagonal of a correlation matrix; that choice is valid only if all unknowns may
assume bounded and valid numeric values which is actually pretty reasonable. But in a rare example of inconsistency in R `cor(x[,3],x[,3])` returns `NA`. Yikes!)] choice in R's
`cov2cor` function, R reports that 
the correlation of `x[,3]` with itself is one, but we don't know the
correlation between `x[,3]` and the other columns.
